---
title: "Analysing US Presidential Election"
output: html_document
---

```{r setup, include=FALSE}
##Libraries 
library(magrittr)
library(dplyr)
library(e1071)
library(cwhmisc)
library(stringr)
library(nnet)
library(pracma)
library(e1071)
library(cwhmisc)
library(ggplot2)
library(randomForest)
library(sqldf)
library(rgdal)
library(readr)
library(scales)
library(kernlab)
library(caret)
setwd("/Users/janhavi 1/Desktop/Digging Into Data/Project")
```

## Data Input
```{r}
setwd("/Users/akshata/Desktop/Digging Into Data/Project")
results<-read.csv("primary_results.csv")
county.demo<-read.csv("county_facts.csv")
dictionary <- read_csv("county_facts_dictionary.csv")
head(results)
head(county.demo)
```

## Generating the Republican Data Frames
```{r}
#setwd("/Users/akshata/Desktop/Digging Into Data/Project")
results<-read.csv("primary_results.csv")
#Separating Republican Results
Republican.votes<-results %>%
  filter(party=="Republican")

#Finding countywise winners for Republicans
countyWinnerR<-Republican.votes %>%
  group_by(state, state_abbreviation,county,fips) %>%
  summarize(winner = candidate[which.max(fraction_votes)],
            fraction_votes = max(fraction_votes),
            votes = max(votes))
countyWinnerR$winner<-factor(countyWinnerR$winner)
head(countyWinnerR)

#Merging county winners and demographics
votesR <- merge(countyWinnerR, county.demo, by = c("fips", "state_abbreviation"))

#Creating Train and Test sets 
index <- 1:nrow(votesR)
testindex <- sample(index, trunc(length(index)/5))
testR <- votesR[testindex,]
trainR <- votesR[-testindex,]
```

## Generating the Democratic Data Frames
```{r}
#Separating Democratic Results
Democrats.votes<-results %>%
  filter(party=="Democrat")

#Finding countywise winners for Democrats
countyWinnerD<-Democrats.votes %>%
  group_by(state,state_abbreviation,county,fips) %>%
  summarize(winner = candidate[which.max(fraction_votes)],
            fraction_votes = max(fraction_votes),
            votes = max(votes))
countyWinnerD$winner<-factor(countyWinnerD$winner)
head(countyWinnerD)

#Merging county winners and demographics
votesD <- merge(countyWinnerD, county.demo, by = c("fips", "state_abbreviation"))

#Creating Train and Test sets 
index <- 1:nrow(votesD)
testindex <- sample(index, trunc(length(index)/5))
testD <- votesD[testindex,]
trainD <- votesD[-testindex,]
```

## Analysing Trends
```{r}
library(plyr)
library(rgeos)
library(rgdal)
library(maptools)
library(maps)
library(RColorBrewer)
library(gpclib)
stateAbbreviation <- "IA"
primaryResults <- read.csv("primary_results.csv")
counties <- readOGR(dsn="county_shapefiles", layer="cb_2014_us_county_500k")


counties@data$id <- rownames(counties@data)
counties.points <- fortify(counties, region="id")
counties.df <- join(counties.points, counties@data, by="id")

stateFips <- state.fips$fips[state.fips$abb==stateAbbreviation]
state <- primaryResults[primaryResults$state_abbreviation==stateAbbreviation,]$state[[1]]
stateCounties <- counties.df[counties.df$STATEFP==stateFips,]

Plot_Map <- function(stateCounties, primaryResults, stateAbbreviation, party)
{
stateResults <- merge(stateCounties, primaryResults[primaryResults$state_abbreviation==stateAbbreviation & primaryResults$party==party,], by.x="NAME", by.y="county")
stateResults <- stateResults[order(stateResults$order),]

p <- ggplot(stateResults) + 
  aes(long,lat,group=group,fill=fraction_votes) + 
  geom_polygon() +
  geom_path(color="white") +
  facet_wrap(~candidate) +
  coord_equal() +
  scale_fill_gradientn(name="Votes",
                       colours=brewer.pal(11,"RdYlGn"),
                       labels=percent) + 
  theme_light(base_size=16) +
  theme(strip.text.x = element_text(size=10, colour="black"),
        strip.background = element_rect(colour="white", fill="white"),
        axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),axis.title.y=element_blank(),
        panel.background=element_blank(),panel.border=element_blank(),panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),plot.background=element_blank()) +
  ggtitle(paste("2016", state, party, "Primary Results"))
return(p)
}

plot_R<-Plot_Map(stateCounties, primaryResults, stateAbbreviation, "Republican")
print(plot_R)
plot_D<-Plot_Map(stateCounties, primaryResults, stateAbbreviation, "Democrat")
print(plot_D)
```

### Number of counties won per state for Republicans 
```{r}
stateCountR<-sqldf('select state,winner,count(winner) as countyswon from countyWinnerR group by state,winner')
ggplot(data = stateCountR, aes(x = state , y = countyswon  , group = winner, fill = winner)) + geom_bar(stat = "identity", width = 0.75, position = "dodge") + ggtitle("Republican Party - Statewise Winners") + theme(axis.text.x = element_text(angle = 90))+ ylab("Number of Countys Won") + xlab("State")
```

### Number of counties won per state for Democrats 
```{r}
stateCountD<-sqldf('select state,winner,count(winner) as countyswon from countyWinnerD group by state,winner')
ggplot(data = stateCountD, aes(x = state , y = countyswon  , group = winner, fill = winner)) + geom_bar(stat = "identity", width = 0.75, position = "dodge")+ ggtitle("Democratic Party - Statewise Winners") + theme(axis.text.x = element_text(angle = 90)) + ylab("Number of Countys Won") + xlab("State")
```

### County wins plotted against county demographics
```{r}
Demographics <- county.demo %>%
    filter(state_abbreviation %in% c("IA", "NV", "SC", "AL", "NH")) %>% 
    select(state_abbreviation = state_abbreviation, county = area_name, 
           median_income = INC110213, per_capita_income = INC910213, hispanic = RHI725214, poverty=PVY020213, white= RHI825214, college = EDU685213, highschool = EDU635213, density = POP060210, female = SEX255214, black=RHI225214) %>% 
   mutate(county = gsub(" County", "", county))

countyWinnerD_Demographics <- merge(countyWinnerD, Demographics, by = c("state_abbreviation", "county"))
countyWinnerR_Demographics <- merge(countyWinnerR, Demographics, by = c("state_abbreviation", "county"))
```

### Effect of Education and Population below poverty level
```{r}
ggplot(data=countyWinnerD_Demographics, aes(x = poverty , y = highschool,color = winner)) + geom_point()+ ggtitle("Democrat County Winners by Poverty level and Educational Attainment") + xlab("People Below Poverty Level %") + ylab("People With High School Education or More %")

ggplot(data=countyWinnerR_Demographics, aes(x = poverty , y = highschool,color = winner)) + geom_point()+ ggtitle("Republican County Winners by Poverty level and Educational Attainment") + xlab("People Below Poverty Level %") + ylab("People With High School Education or More %")
```

### Effect of Median Househod Income and Race
```{r}
ggplot(data=countyWinnerD_Demographics, aes(x = median_income , y = black,color = winner)) + geom_point()+ ggtitle("Democrat County Winners by African American population and Median Income") + xlab("Median Household Income") + ylab("African American Population %")

ggplot(data=countyWinnerR_Demographics, aes(x = median_income , y = black,color = winner)) + geom_point()+ ggtitle("Reoublican County Winners by African American population and Median Income") + xlab("Median Household Income") + ylab("African American Population %")
```


### Corelations between demographics and number of votes for Individual Candidates
```{r}
data <- merge(results,county.demo, by="fips")

candidateList <- c("Hillary Clinton","Bernie Sanders","Donald Trump","Marco Rubio","Ted Cruz")
                    
for(candidate in candidateList) 
{
  candidate_cor <- data.frame("var"=dictionary$description, "name"=dictionary$column_name)
  candidate_cor$cor <- c(cor(data[data$candidate==candidate,]$fraction_votes,
                             data[data$candidate==candidate, dictionary$column_name]))
  candidate_cor <- candidate_cor[order(candidate_cor$cor),]
  candidate_cor$var <- factor(candidate_cor$var, levels=candidate_cor$var)
  p <- ggplot(candidate_cor, aes(x=var, y=cor, color= cor)) + 
    geom_point(stat="identity") +
    coord_flip() + 
    ylab("Correlation") + xlab("") +
    theme(axis.text = element_text(size=6),
          axis.title = element_text(size=6),
          title = element_text(size=8)) +
    ggtitle(paste0(candidate, " : Correlation Between Votes & County Demographics"))
  print(p)
}
```

### Correlation between Demographics
```{r}
merged<-read.csv("merged.csv")

Republican.votes<-merged %>%
  filter(party=="Republican")

Democrats.votes<-merged %>%
  filter(party=="Democrat")

# Finding correlation between Race variables
#--------------------------------------------------------------------------
library(corrplot)
library(caret)
raceR<-Republican.votes[, c(20:27)]
raceR.corr<-cor(raceR)
corrplot(raceR.corr)
findCorrelation(raceR.corr, cutoff = .50, verbose = TRUE, names = TRUE, exact = TRUE)

raceD<-Democrats.votes[, c(20:27)]
raceD.corr<-cor(raceD)
corrplot(raceD.corr)
findCorrelation(raceD.corr, cutoff = .50, verbose = TRUE, names = TRUE, exact = TRUE)
#----------------------------------------------------------------------------
# Finding correlation between Education Variables
educationR<-Republican.votes[, c(31:32)]
educationR.corr<-cor(educationR)
corrplot(educationR.corr)
findCorrelation(educationR.corr, cutoff = .50, verbose = TRUE, names = TRUE, exact = TRUE)
#----------------------------------------------------------------------------
# Finding correlation between Education Variables and Veteran variable
educationVR<-Republican.votes[, c(31:33)]
educationVR.corr<-cor(educationVR)
corrplot(educationVR.corr)
findCorrelation(educationVR.corr, cutoff = .60, verbose = TRUE, names = TRUE, exact = TRUE)

#----------------------------------------------------------------------------------------
findCorrelation(educationR.corr, cutoff = .50, verbose = TRUE, names = TRUE, exact = TRUE)
#Finding correlation between Race and Education variables
eduraceR<-Republican.votes[,c(21,22,23,24,26,31)]
eduraceR.corr<-cor(eduraceR)
corrplot(eduraceR.corr)
findCorrelation(eduraceR.corr, cutoff = .60, verbose = TRUE, names = TRUE, exact = TRUE)
#---------------------------------------------------------------------------
# Finding correlation between age and sex variables
agesexR<-Republican.votes[, c(16:19)]
agesexR.corr<-cor(agesexR)
corrplot(agesexR.corr)
findCorrelation(agesexR.corr, cutoff = .60, verbose = TRUE, names = TRUE, exact = TRUE)
#-----------------------------------------------------------------------------
#Finding correlation between Age, Sex(Females only), Education and Race Variables
ASER<-Republican.votes[, c(18,19,22,23,26,32)]
ASER.corr<-cor(ASER)
corrplot(ASER.corr)
findCorrelation(ASER.corr, cutoff = .60, verbose = TRUE, names = TRUE, exact = TRUE)
#------------------------------------------------------------------------------
#Finding correlation between population variables
popR<-Republican.votes[, c(12:15)]
pop.corr<-cor(popR)
corrplot(pop.corr)
findCorrelation(pop.corr, cutoff = .60, verbose = TRUE, names = TRUE, exact = TRUE)
#-------------------------------------------------------------------------------
#Finding correlation between Age, Education and Race Variables
AER<-Republican.votes[, c(18,22,23,26,32)]
AER.corr<-cor(AER)
corrplot(AER.corr)
findCorrelation(AER.corr, cutoff = .60, verbose = TRUE, names = TRUE, exact = TRUE)
#---------------------------------------------------------------------------------
#Finding correlation between Race and Poverty level

RP<-Republican.votes[, c(21,22,23,24,26,43)]
RP.corr<-cor(RP)
corrplot(RP.corr)
findCorrelation(RP.corr, cutoff = .60, verbose = TRUE, names = TRUE, exact = TRUE)
#----------------------------------------------------------------------------------
#Finding correlation between Race and Income variables
eduraceR<-Republican.votes[,c(26,41,42)]
eduraceR.corr<-cor(eduraceR)
corrplot(eduraceR.corr)
findCorrelation(eduraceR.corr, cutoff = .60, verbose = TRUE, names = TRUE, exact = TRUE)
#-------------------------------------------------------------------------------------
#Finding correlation between Hispanic and Poverty variables
eduraceR<-Republican.votes[,c(26,43)]
eduraceR.corr<-cor(eduraceR)
corrplot(eduraceR.corr)
findCorrelation(eduraceR.corr, cutoff = .60, verbose = TRUE, names = TRUE, exact = TRUE)
#----------------------------------------------------------------------------------------
#Finding correlation between Hispanic and Poverty, and age 65+ variables, education (Highschool)
eduraceR<-Republican.votes[,c(26,43,31,18)]
eduraceR.corr<-cor(eduraceR)
corrplot(eduraceR.corr)
findCorrelation(eduraceR.corr, cutoff = .70, verbose = TRUE, names = TRUE, exact = TRUE)
#----------------------------------------------------------------------------------------
#Finding correlation between white and education (Bachelor)
eduraceR<-Republican.votes[,c(20,32)]
eduraceR.corr<-cor(eduraceR)
corrplot(eduraceR.corr)
findCorrelation(eduraceR.corr, cutoff = .70, verbose = TRUE, names = TRUE, exact = TRUE)
#----------------------------------------------------------------------------------------
```

## Republican Predictive Models
```{r}
Function_Prediction <- function(testdata, model){
  testdata$Predicted  <- predict(model, testdata)
  misClassificError_glm_2 <- mean(testdata$Predicted != testdata$winner)
  return(1-misClassificError_glm_2)
}
#library(kernlab)
#Model 1 
#Inputs: White alone, White alone(pop above 18yrs), African American, Persons below Poverty Level, High School Graduates, (25 yrs+), Bachelor???s degree, (25 yrs+), Under 18yrs, Per capita money income in past 12 months, Median household income 
LR_TEST1 <- Function_Prediction(testR, (multinom(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+AGE295214+INC910213+INC110213, data=trainR)))


SVM_RAD_TEST1 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+AGE295214+INC910213+INC110213, data=trainR,kernel= "rbfdot")))

SVM_VD_TEST1 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+AGE295214+INC910213+INC110213, data=trainR,kernel= "vanilladot")))

SVM_LP_TEST1 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+AGE295214+INC910213+INC110213, data=trainR,kernel= "laplacedot")))

SVM_BD_TEST1 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+AGE295214+INC910213+INC110213, data=trainR,kernel= "besseldot")))

Model1_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), Model_1= c(LR_TEST1, SVM_RAD_TEST1, SVM_VD_TEST1, SVM_LP_TEST1, SVM_BD_TEST1))

#Model 2
#Inputs: White alone, African American, Persons below Poverty Level, High School Graduates, (25 yrs+), Bachelor???s degree, (25 yrs+), Under 18yrs, 65 yrs+, Per capita money income in past 12 months, Median household income, Population per Square mile 
LR_TEST2 <- Function_Prediction(testR, (multinom(winner ~ RHI825214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+AGE295214+INC910213+INC110213+POP060210, data=trainR)))

SVM_RAD_TEST2 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+AGE295214+INC910213+INC110213+POP060210, data=trainR,kernel= "rbfdot")))

SVM_VD_TEST2 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+AGE295214+INC910213+INC110213+POP060210, data=trainR,kernel= "vanilladot")))

SVM_LP_TEST2 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+AGE295214+INC910213+INC110213+POP060210, data=trainR,kernel= "laplacedot")))

SVM_BD_TEST2 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+AGE295214+INC910213+INC110213+POP060210, data=trainR,kernel= "besseldot")))

Model2_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), Model_2= c(LR_TEST2, SVM_RAD_TEST2, SVM_VD_TEST2, SVM_LP_TEST2, SVM_BD_TEST2))

#Model 3
#Inputs: White alone, African American+White alone(pop above 18yrs), Persons below Poverty Level,High School Graduates, (25 yrs+), Bachelor???s degree, (25 yrs+), 65 yrs+, Per capita money income in past 12 months 
LR_TEST3 <- Function_Prediction(testR, (multinom(winner ~ RHI825214+RHI125214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+INC910213, data=trainR)))

SVM_RAD_TEST3 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI125214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+INC910213, data=trainR,kernel= "rbfdot")))

SVM_VD_TEST3 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI125214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+INC910213, data=trainR,kernel= "vanilladot")))

SVM_LP_TEST3 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI125214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+INC910213, data=trainR,kernel= "laplacedot")))

SVM_BD_TEST3 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI125214+RHI225214+PVY020213+EDU685213+EDU635213+AGE775214+INC910213, data=trainR,kernel= "besseldot")))

Model3_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), Model_3= c(LR_TEST3, SVM_RAD_TEST3, SVM_VD_TEST3, SVM_LP_TEST3, SVM_BD_TEST3))

#Model 4
#Inputs: Hispanic or Latino, Persons below Poverty Level, High School Graduates, (25 yrs+), Bachelor???s degree, (25 yrs+), Under 18 yrs+ Female persons
LR_TEST4 <- Function_Prediction(testR, (multinom(winner ~ RHI725214+PVY020213+EDU685213+EDU635213+AGE295214+SEX255214+POP815213+POP645213, data=trainR)))

SVM_RAD_TEST4 <- Function_Prediction(testR, (ksvm(winner ~ RHI725214+PVY020213+EDU685213+EDU635213+AGE295214+SEX255214+POP815213+POP645213, data=trainR,kernel= "rbfdot")))

SVM_VD_TEST4 <- Function_Prediction(testR, (ksvm(winner ~ RHI725214+PVY020213+EDU685213+EDU635213+AGE295214+SEX255214+POP815213+POP645213, data=trainR,kernel= "vanilladot")))

SVM_LP_TEST4 <- Function_Prediction(testR, (ksvm(winner ~ RHI725214+PVY020213+EDU685213+EDU635213+AGE295214+SEX255214+POP815213+POP645213, data=trainR,kernel= "laplacedot")))

SVM_BD_TEST4 <- Function_Prediction(testR, (ksvm(winner ~ RHI725214+PVY020213+EDU685213+EDU635213+AGE295214+SEX255214+POP815213+POP645213, data=trainR,kernel= "besseldot")))

Model4_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), Model_4= c(LR_TEST4, SVM_RAD_TEST4, SVM_VD_TEST4, SVM_LP_TEST4, SVM_BD_TEST4))

#Model 5
#Inputs: White alone(pop above 18yrs), African American, White alone, Persons below Poverty Level, Bachelor???s degree, (25 yrs+), High School Graduates, (25 yrs+) ,Per capita money income in past 12 months, Median household income 
LR_TEST5 <- Function_Prediction(testR, (multinom(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+INC910213+INC110213, data=trainR)))

SVM_RAD_TEST5 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+INC910213+INC110213, data=trainR,kernel= "rbfdot")))

SVM_VD_TEST5 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+INC910213+INC110213, data=trainR,kernel= "vanilladot")))

SVM_LP_TEST5 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+INC910213+INC110213, data=trainR,kernel= "laplacedot")))

SVM_BD_TEST5 <- Function_Prediction(testR, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+INC910213+INC110213, data=trainR,kernel= "besseldot")))

Model5_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), Model_5= c(LR_TEST5, SVM_RAD_TEST5, SVM_VD_TEST5, SVM_LP_TEST5, SVM_BD_TEST5))

Accuracy_1 <- merge(Model1_Accuracies, Model2_Accuracies, by = c("Algorithms"))
Accuracy_2 <- merge(Model3_Accuracies, Model4_Accuracies, by = c("Algorithms"))
Accuracy_3 <- merge(Accuracy_1, Accuracy_2, by = c("Algorithms"))
Accuracy <- merge(Accuracy_3, Model5_Accuracies, by = c("Algorithms"))


```

### Republican Model Accuracies
```{r}
Accuracy
```

## Democrat Predictive Models
```{r}
Function_Prediction <- function(testdata, model){
  testdata$Predicted  <- predict(model, testdata)
  misClassificError_glm_2 <- mean(testdata$Predicted != testdata$winner)
  return(1-misClassificError_glm_2)
}
#library(kernlab)
#Model 1 
#Inputs: White Alone, 65 yrs, Bachelor???s degree, (25 yrs+), Median household income 
LR_TEST1 <- Function_Prediction(testD, (multinom(winner ~ RHI825214+RHI125214+EDU685213+INC110213+AGE775214, data=trainD)))

SVM_RAD_TEST1 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213+INC110213+AGE775214, data=trainD,kernel= "rbfdot")))

SVM_VD_TEST1 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213+INC110213+AGE775214, data=trainD,kernel= "vanilladot")))

SVM_LP_TEST1 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213+INC110213+AGE775214, data=trainD,kernel= "laplacedot")))

SVM_BD_TEST1 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213+INC110213+AGE775214, data=trainD,kernel= "besseldot")))

Model1_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), MOdel_1= c(LR_TEST1, SVM_RAD_TEST1, SVM_VD_TEST1, SVM_LP_TEST1, SVM_BD_TEST1))

#Model 2
#Inputs: White alone, Bachelor???s degree, (25 yrs+), White alone(Not Hispanic or Latino) 
LR_TEST2 <- Function_Prediction(testD, (multinom(winner ~ RHI825214+RHI125214+EDU685213, data=trainD)))

SVM_RAD_TEST2 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213, data=trainD,kernel= "rbfdot")))

SVM_VD_TEST2 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213, data=trainD,kernel= "vanilladot")))

SVM_LP_TEST2 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213, data=trainD,kernel= "laplacedot")))

SVM_BD_TEST2 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213, data=trainD,kernel= "besseldot")))

Model2_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), Model_2= c(LR_TEST2, SVM_RAD_TEST2, SVM_VD_TEST2, SVM_LP_TEST2, SVM_BD_TEST2))

#Model 3
#Inputs: White alone, Bachelor???s degree, (25 yrs+), 65 yrs
LR_TEST3 <- Function_Prediction(testD, (multinom(winner ~ RHI825214+RHI125214+EDU685213+AGE775214 , data=trainD)))

SVM_RAD_TEST3 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213+AGE775214, data=trainD,kernel= "rbfdot")))

SVM_VD_TEST3 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213+AGE775214, data=trainD,kernel= "vanilladot")))

SVM_LP_TEST3 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213+AGE775214, data=trainD,kernel= "laplacedot")))

SVM_BD_TEST3 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI125214+EDU685213+AGE775214, data=trainD,kernel= "besseldot")))

Model3_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), Model_3= c(LR_TEST3, SVM_RAD_TEST3, SVM_VD_TEST3, SVM_LP_TEST3, SVM_BD_TEST3))

#Model 4
#Inputs: African American, White alone, 65 yrs + ,Bachelor???s degree, (25 yrs+), Median household income 
LR_TEST4 <- Function_Prediction(testD, (multinom(winner ~ RHI225214+RHI125214+EDU685213+AGE775214+EDU685213+INC110213, data=trainD)))

SVM_RAD_TEST4 <- Function_Prediction(testD, (ksvm(winner ~ RHI225214+RHI125214+EDU685213+AGE775214+EDU685213+INC110213, data=trainD,kernel= "rbfdot")))

SVM_VD_TEST4 <- Function_Prediction(testD, (ksvm(winner ~ RHI225214+RHI125214+EDU685213+AGE775214+EDU685213+INC110213, data=trainD,kernel= "vanilladot")))

SVM_LP_TEST4 <- Function_Prediction(testD, (ksvm(winner ~ RHI225214+RHI125214+EDU685213+AGE775214+EDU685213+INC110213, data=trainD,kernel= "laplacedot")))

SVM_BD_TEST4 <- Function_Prediction(testD, (ksvm(winner ~ RHI225214+RHI125214+EDU685213+AGE775214+EDU685213+INC110213, data=trainD,kernel= "besseldot")))

Model4_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), Model_4= c(LR_TEST4, SVM_RAD_TEST4, SVM_VD_TEST4, SVM_LP_TEST4, SVM_BD_TEST4))

#Model 5
#Inputs:White alone, White alone(pop above 18yrs), African American+High School Graduates, (25 yrs+), Bachelor???s degree, (25 yrs+), Under 18yrs 
LR_TEST5 <- Function_Prediction(testD, (multinom(winner ~ RHI825214+RHI225214+RHI125214+EDU685213+EDU635213+AGE295214, data=trainD)))

SVM_RAD_TEST5 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+EDU685213+EDU635213+AGE295214, data=trainD,kernel= "rbfdot")))

SVM_VD_TEST5 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+EDU685213+EDU635213+AGE295214, data=trainD,kernel= "vanilladot")))

SVM_LP_TEST5 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+EDU685213+EDU635213+AGE295214, data=trainD,kernel= "laplacedot")))

SVM_BD_TEST5 <- Function_Prediction(testD, (ksvm(winner ~ RHI825214+RHI225214+RHI125214+EDU685213+EDU635213+AGE295214, data=trainD,kernel= "besseldot")))
Model5_Accuracies <- data.frame(Algorithms = c("Logistic Regression", "SVM Radial","SVM Linear","SVM Laplacian", "SVM Bessel"), Model_5= c(LR_TEST5, SVM_RAD_TEST5, SVM_VD_TEST5, SVM_LP_TEST5, SVM_BD_TEST5))

Accuracy_1 <- merge(Model1_Accuracies, Model2_Accuracies, by = c("Algorithms"))
Accuracy_2 <- merge(Model3_Accuracies, Model4_Accuracies, by = c("Algorithms"))
Accuracy_3 <- merge(Accuracy_1, Accuracy_2, by = c("Algorithms"))
Accuracy <- merge(Accuracy_3, Model5_Accuracies, by = c("Algorithms"))
```

### Democrat Model Accuracies
```{r}
Accuracy
```

## Evaluating Final Models 
```{r}
county.demo<-read.csv("county_facts.csv")
maryland_Demo <- county.demo %>%
  filter(state_abbreviation=="MD")
###Output For Maryland

## Republic 
Final_Republican_Model <- (ksvm(winner ~ RHI825214+RHI225214+RHI125214+PVY020213+EDU685213+EDU635213+AGE295214+INC910213+INC110213, data=trainR,kernel= "rbfdot"))
testR$Predicted  <- predict(Final_Republican_Model, testR)
confusionMatrix(testR$Predicted, testR$winner)

## Democratic
Final_Democratic_Model <- (ksvm(winner ~ RHI825214+RHI225214+RHI125214+EDU685213+EDU635213+AGE295214,data=trainD,kernel= "rbfdot"))
testD$Predicted  <- predict(Final_Democratic_Model, testD)
confusionMatrix(testD$Predicted, testD$winner)

maryland_Demo$Predicted_Republican <- predict(Final_Republican_Model,maryland_Demo)
maryland_Demo$Predicted_Democratic <- predict(Final_Democratic_Model, maryland_Demo)
```

### Maryland Primaries Predictions
```{r}
#Republicans
summary(maryland_Demo$Predicted_Republican)
#Democrats
summary(maryland_Demo$Predicted_Democratic)
write.csv(maryland_Demo,"Maryland_Predicted_Final.csv")
